Paper_analyses

### 2021-07-22 Paper_Analyses_subj_obje_arousal.Rmd
smooth pupil velocity
to do smooth pupil velocity

>>>>

Velocity test

```{r}
nrow(nbins)
nbins = 30 # number of bins
unique(tmp.df4_full_stim_downs_jun2021_with_behnew$ssid)
tmp.df4_full_stim_downs_jun2021_with_behnew <- tmp.df4_full_stim_downs_jun2021_with_behnew%>%
  group_by(ssid, tNo)%>%
  arrange(ssid,tNo, timerezero3)%>%
  mutate(pup_vel_smooth = zoo::rollmean(pup_velocity, k = 3, fill = NA))

zoo::rollmean(pup_velocity, k = 3, fill = NA)

tmp.df4_full_stim_downs_jun2021_with_behnew$pup_vel_smooth

# create and empty dataframe for the timecourse analyses
timecourse_result_df_int_vel <- data.frame(timebins= rep(NA, 30), Estimate= rep(NA, 30), 
                                   t=rep(NA, 30), p=rep(NA, 30), cov= as.character(rep(NA,30)))

rm(b)

for (b in 3:length(nbins)) {
  # for (s in 1:length(nsim)) {

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
        lmer_bin_pup  <- lmer(pup_vel_smooth ~ arousal_c* valence+Mean_gray_z  +
                                (1 | ssid)+
                                (0 +arousal_c* valence | ssid),
                                # (1|stimIAPS),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
                                    # mediansplit_self_valence == "More positive" & 
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            lmer_bin_pup_summary
            # lmer_bin_pup_summary[["coefficients"]][3,1]
            timecourse_result_df_int_vel[i,1]<- tmp.df4_full_stim_downs_jun2021_with_behnew$timerezero3[b] #save the exact value of time bin
            timecourse_result_df_int_vel[i,2]<- lmer_bin_pup_summary[["coefficients"]][2,1] # first number is term(row), second is column
            timecourse_result_df_int_vel[i,3]<-lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_result_df_int_vel[i,4]<-lmer_bin_pup_summary[["coefficients"]][2,5] # p value
            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
            timecourse_result_df_int_vel[i,5] <-ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

timecourse_result_df_int_vel %>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)+
  geom_vline(xintercept = 1, color = 'red')
  # ylim(-4,4)

??ma
?stats::filter
tmp.df4_full_stim_downs_jun2021_with_behnew%>%
  subset(ssid == 310 & tNo == 10)%>%
  ggplot(aes(timerezero3,zoo::rollmean(pup_velocity, k = 3, fill = NA)))+
  geom_line()+
  geom_line(aes(y = pup_velocity), color = 'red')+
  geom_smooth(se = F)

tmp.df4_full_stim_downs_jun2021_with_behnew%>%
  subset(ssid == 310 & tNo == 15)%>%
  ggplot(aes(timerezero3,pup_basCor))+
  geom_point()+
  # geom_line(aes(y = pup_velocity), color = 'red')+
  geom_smooth(se = F)
